---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: serif;
  background-color: #ADD8E6;
}

p {
font-size: 20px;
}

```

## Observation of the features of Ads on Youtube Videos

```{r}
library(tidyverse)
# read in data
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vR_7onUBm866lQhkIdG9BkRjjBqQTftFDPhY5n1vo6ehOAN0Lk5hNoz2AxcNXp9o372pND_GEoDAcAc/pub?gid=269772251&single=true&output=csv")
latest_data <- logged_data %>%
  rename(ad = 2,
         when_ad = 3,
         ad_length = 4,
         skip = 5,
         skip_length = 6, 
         video_length = 7, 
         video_views = 8)

mean_skip_length <- latest_data$skip_length %>% mean(na.rm=TRUE) %>% round(1)

max_ad_length <- latest_data$ad_length %>% max()
min_ad_length <- latest_data$ad_length %>% min()
mean_ad_length <- latest_data$ad_length %>% mean() %>% round(1)

# mean length of ad for when the ad is skippable and it isn't 
mean_ad_no_skip <- latest_data$ad_length[latest_data$skip == "No"] %>% mean() %>% round(1)
mean_ad_yes_skip <- latest_data$ad_length[latest_data$skip == "Yes"] %>% mean() %>% round(1)

# mean length of video when ad is skippable and it isn't
mean_video_no_skip <- latest_data$video_length[latest_data$skip == "No"] %>% mean() %>% round(1)
mean_video_yes_skip <- latest_data$video_length[latest_data$skip == "Yes"] %>% mean() %>% round(1)


latest_data %>%
  ggplot() +
  geom_bar(aes(x = ad_length,
               fill = skip)) +
  labs(title = "Length of Ad compared to whether it could be skipped",
       x = "Ad Length (in seconds)",
       y = "Frequency",
       caption = "Source: Project 2 Survey")

latest_data %>%
  ggplot() +
  geom_bar(aes(x = when_ad), 
           fill = c("red","blue","green")) +
  labs(title = "Frequency of when the Ad was presented", 
       x = "Presentation of Ad", 
       y = "Frequency",
       caption = "Source: Project 2 Survey")
```


For the ads that were skippable, the mean length of time before the skip button was presented was `r mean_skip_length` seconds.

The maximum length of an ad was `r max_ad_length` seconds, while the minimum length was `r min_ad_length` seconds, and the mean ad length was `r mean_ad_length`

The mean length of the ad when the ad was skippable was `r mean_ad_yes_skip` seconds, while the mean length of an ad when it was not skippable was lower at `r mean_ad_no_skip` seconds. 

The mean length of the video when the ad was skippable was `r mean_video_yes_skip` seconds, while the mean length of a video when it was not skippable was higher at `r mean_video_no_skip` seconds. 

